Case Study (McKenna)

### 2020-05-18 Code/mrp/Case Study (McKenna) .Rmd
Addressing errors in McKenna Logit model

#### McKenna's logit model  
```{r}
predictors <- sample %>% 
  select(male, age, eth, income, state)

pred <- as.matrix(predictors, byrow = TRUE)
```

```{r}
data_list <- list(
  D = 5,                                              # Number of variables. 
  N = 1200,                                           # Number of observations.
  L = 6300,                                           # Number of groups. 
  y = sample$service_failure,                         # Outcome variables. 
  ll = sample(6300, 1200, replace = TRUE),            # Group assignment. 
  x = predictors                                      # Matrix of predictors. 
)
```

@@

```{r, eval = FALSE}
stanfit_final <- stan(file = "downes_copy.stan",
                        data = downes_list, 
                        iter = n_iter, chains = n_chain)
```
#### Stan user guide logit model 
```{r}
stan_data <- list( 
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income, 
  male = sample$male, 
  state = sample$state, 
  Y = sample$service_failure, 
  N = length(sample$service_failure))
```

>>>>

#### McKenna's logit model  
- The issue here is the way that the matrix of predictors is being specified, I think 
```{r}
predictors <- sample %>% 
  select(male, age, eth, income, state)

pred <- as.matrix(predictors)

# pred <- list()
# for (n in 1:nrow(predictors)) {
#   pred[[n]] <- matrix(as.numeric(predictors[n,]))
# }
```

```{r}
data_list <- list(
  D = 5,                                              # Number of variables. 
  N = 1200,                                           # Number of observations.
  L = 5,                                              # Number of groups. 
  y = sample$service_failure,                         # Outcome variables. 
  ll = sample(5, 1200, replace = TRUE),               # Group assignment. 
  x = pred                                            # Matrix of predictors. 
)
```

@@

```{r, eval = FALSE}
stanfit_final <- stan(file = "downes_copy.stan",
                        data = downes_list, 
                        iter = n_iter, chains = 1)
```
#### Stan user guide logit model 
```{r}
stan_data <- list( 
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income, 
  male = sample$male, 
  state = sample$state, 
  Y = sample$service_failure, 
  N = length(sample$service_failure)
  )
```
